Accurate evaluation of dislocation tractions

### 2020-11-18 src/wip/DanielCelisGarza/Accurate_evaluation_of_dislocation_tractions/paper/main.tex
Editing

From \cref{f:head_vs_ana_vs_num_eperp,f:head_vs_ana_vs_num_epar,f:head_vs_ana_vs_num_screw} it seems
like both analytic and numeric tractions are both appropriate in most cases. At least at these scales, there is only one instance where numeric tractions yield very incorrect results. Although these can have significant consequences later in a simulation's runtime, and particularly in simulations where dislocations regularly come into close contact with surfaces.

@@

In order to show the effects numerical tractions have on simulations, we ran a very simple cantilever bending simulation where the only difference was the traction calculation method. A very simple yet illustrative qualitative example is to produce a scatter plot of the numerically calculated tractions vs analytically calculated tractions at any time during the simulation. To obviate the problem even more, it helps making the axes proportional. What is observed in practically every case, is a positive correlation (though as we have seen in \cref{sf:sxxepar,sf:sxxAepar,sf:sxxNepar}, numerical tractions can produce sign inversions under specific conditions), but the axis that represents the numerically calculated tractions will be visually larger, as numeric tractions produce more extreme values. Statistically speaking, the closer the $R$-value is to 1 and the closer a linear fit is to $y=x$, the more accurate numerical tractions are for any given moment in a simulation. We have yet to find a single example where this happens. Furthermore, the chaotic nature of dislocation dynamics means that slight deviations will yield noticeably different results for the same starting conditions.

>>>>

From \cref{f:head_vs_ana_vs_num_eperp,f:head_vs_ana_vs_num_epar,f:head_vs_ana_vs_num_screw} it seems
like both analytic and numeric tractions are appropriate in most cases. At least at these scales, there is only one instance where numeric tractions yield very incorrect results. Although these can have significant consequences later in a simulation's runtime, and particularly in simulations where dislocations regularly come into close contact with surfaces.

@@

In order to show the effects numerical tractions have on simulations, we ran a very simple simulation where the only difference was the traction calculation method. A very simple yet illustrative qualitative example is to produce a scatter plot of the numerically calculated tractions vs analytically calculated ones at any time during any simulation. To obviate the problem even more, it helps making the axes proportional. What is observed in practically every case, is a positive correlation (though as we have seen in \cref{sf:sxxepar,sf:sxxAepar,sf:sxxNepar}, numerical tractions can produce sign inversions under specific conditions), but the axis that represents the numerically calculated tractions will be visually larger, as numeric tractions produce more extreme values. Statistically speaking, the closer the $R$-value is to 1 and the closer a linear fit is to $y=x$, the more accurate numerical tractions are for any given moment in a simulation. We have yet to find a single example where this happens. Furthermore, the chaotic nature of dislocation dynamics means that slight deviations will yield noticeably different results for the same starting conditions.
